Hypertension and microbiome

### 2019-09-12 articletwo.Rmd
save rds
Minor

dds <- DESeq(ds2, fitType='mean', parallel = TRUE, BPPARAM=MulticoreParam(16))

results(dds) %>%
    as.data.frame %>%
    kable
```

>>>>

dds <- DESeq(ds2, fitType='mean', parallel = TRUE, BPPARAM=MulticoreParam(16))
saveRDS(dds, file = "rds/dds.rds")

dds <- readRDS(file = "rds/dds.rds")

results(dds) %>%
    as.data.frame %>%
    tibble::rownames_to_column("Feature") %>%
    dplyr::mutate(qval = p.adjust(pvalue, method="BH")) %>%
    dplyr::filter(qval < 0.05) %>%
    kable
```
